Age-related changes in plant growth and traits

### 2015-05-20 results_accessory_shorter.Rmd
Rename with correct extension

mod <- lm (log(FinalWeight)~log(PerPropagule), data=subset(SummaryInd,PerPropagule>0))
plot(PerPropagule~FinalWeight,data=subset(SummaryInd,PerPropagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Proportion reproductive investment to propagules",xlim=c(100,2000000),xlab="Total size (mg)")
words.bottom.right.logxy(mod)
text((par("fin")[1]*.5),(par("fin")[2]*.2),"Total size (mg)")
```

>>>>

mod <- lm (log(FinalWeight)~log(PerPropagule), data=subset(SummaryInd,PerPropagule>0))
plot(PerPropagule~FinalWeight,data=subset(SummaryInd,PerPropagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Proportion reproductive investment to propagules",xlim=c(100,2000000),xlab="Total size (mg)")
words.bottom.right.logxy(mod)
mtext("Total size (mg)", 1, outer=TRUE)
```
